Title

### 2013-03-19 inc/laser/laser.tex
tweaks to the laser section

@@

The 250fs ML pulses generated at 3.5W of average output power and a 63.5MHz repetition rate are frequency doubled in a 2mm-thick, Brewster-cut and critically phase-matched Lithium triborate (LBO) crystal.
The resultant efficient frequency doubling, which exceeds 60\% at a ML fundamental power of $\sim$3W, yields 1.65W of average power at 523nm ---
%page 8640
a peak green pulse power of $\sim$130kW.
This femtosecond visible output will be used as the driving pulsed laser radiation source for an ultrafast electron microscope \cite{king_ultrafast_2005}.

>>>>

For most photoemission sources, the fundamental laser output's 1.19 eV photons do not provide enough energy to excite electrons above the vacuum level, either in single or two-photon emission.\cite{eastman_photoelectric_1970,johnson_optical_1972,dowell_quantum_2009}
By appropriate application of crystals with strong non-linear properties, two photons at frequency $\omega$ may be converted into one photon at frequency $2 \omega$.\cite{shen_principles_2002}
Since these higher harmonics will be necessary for stimulating photoemission it is important to optimize and characterize the efficiency of this process.

@@

The 250fs ML pulses generated at 3.5W of average output power and a 63.5MHz repetition rate are frequency doubled in a 2mm-thick, Brewster-cut and critically phase-matched Lithium triborate (LBO) crystal.
The resultant efficient frequency doubling, which exceeds 60\% at a ML fundamental power of $\sim$3W, yields 1.65W of average power at 523nm ---
%page 8640
a peak green pulse power of $\sim$130kW.
This laser is the short-pulse photon source used to photoemit electrons for all the experimental results shown in this thesis.
